Topological Equivariant Artist Model for Visualization Library Architecture

### 2022-05-29 paper/main.tex
xi figure caption

\begin{figure}[h!]
  \includegraphics*[width=1\columnwidth]{xi_scatter.png}
  \caption{The graphic base space $\gbase_{0}$ constracts to the data base space $\dbase_{0}$, and $\gbase_{1}$ contracts to $\dbase_{1}$. Therefore the data section $\dsection(\dbase_{0})$ can be copied over such that every pulled back section evaluates to the same record $\vindexpull\dsection|_{\gbase_{0}} = \dsection_{\dbasepoint_{0}}$. Each of these pulled back sections $\vindexpull(\gbasepoint_i)$ has a corresponding graphic section $\gsection(\gbasepoint_i)$ that returns a record in an idealized prerendered infinite resolution space. Here we approximate that space and show $\gsection|_{\gbase_0}, \gsection|_{\gbase_1}$ to show how a section produces a visual element that has corresponding data. The way each element is parameterized is encapsulated in the pushforward $\vindexpush\gsection$. The pushforward is the curried section $\gsection|_{\vindexpre(\dbasepoint)}$, so we've chosen to represent x and y in data units and color in hex as an example of the type of parameterization encapsulated in the function. \label{fig:atct:morphisms:sheaf}}
\end{figure}

Functors between sheaves are a way of expressing the bookkeeping involved in keeping track of which graphic section corresponds to which data section. The $(\dbasepoint_i, \gbase_i)$ pairing expressed in \autoref{eq:atct:xi} establishes that there is a correspondence between sections evaluated over $\dbasepoint_i$ and $\gbase_i$. This allows us to construct graphic specifications for each data index $\vindexpush\gsection$ and retrieve the data $\vindexpull\dsection$ for any graphic section generating any piece of a graphic. In \autoref{fig:atct:morphisms:sheaf}, the sections return rows in the table from \autoref{fig:related-work:continuity:ktypes}. Each section $\dsection(\dbasepoint_{i})$ has a corresponding visual element produced by evaluating the graphic section on the graphic base space $\gsection|_{\gbase_{i}}$. In \autoref{fig:atct:morphisms:sheaf} the output of $\gsection$ as pixels in an idealized prerendered space is approximated as the circles. Each graphic section $\gsection(\gbasepoint), \gbasepoint \in \gbase_{i}$ that is a piece of the graphic has a corresponding pulled back data value $\vindexpull\dsectionc(\gbasepoint)$. The pullback copies the data points such that $\vindexpull\dsectionc|_{\gbase_i} = \dsection(\dbasepoint_i)$. Each visual element $\gsection|_{\gbase_i}$ is generated from a single record $\dsection(\dbasepoint_i)$; therefore the pushforward is the curried graphic section $\gsection|_{\vindexpre(\dbasepoint_i)}$. The graphic parameterized in \autoref{fig:atct:morphisms:sheaf} is intended as an approximation of $\vindexpush\gsection$.

>>>>

\begin{figure}[h!]
  \includegraphics*[width=1\columnwidth]{xi_scatter.png}
  \caption{The functors $\vindex, \vindexpull, \vindexpush$ establish the correspondence between a data section \dsection\ and a graphic generation function \gsection. For every data record $\dsection(\dbasepoint)$, there is a graphic generating function $\vindexpush\gsection = \gsection|_{\vindexpre\dbasepoint}$. This curried function is here represented as the visual parameters associated with that function to demonstrate that it generates the visual element for that data record. Every data section can also be copied over to the graphic space such that each piece of the (idealized in infinite resolution) graphic $\gsection(\dbasepoint)$ has a corresponding data value $\vindexpull\dsection(\dbasepoint)$.
  \label{fig:atct:morphisms:sheaf}}
\end{figure}

Functors between sheaves are a way of expressing the bookkeeping involved in keeping track of which graphic section \gsection\ corresponds to which data section \dsection\. The $(\dbasepoint_i, \gbase_i)$ pairing expressed in \autoref{eq:atct:xi} establishes that there is a correspondence between sections evaluated over $\dbasepoint_i$ and $\gbase_i$. This allows us to construct graphic specifications for each data index $\vindexpush\gsection$ and retrieve the data $\vindexpull\dsection$ for any graphic section generating any piece of a graphic. In \autoref{fig:atct:morphisms:sheaf}, the sections return rows in the table from \autoref{fig:related-work:continuity:ktypes}. Each section $\dsection(\dbasepoint_{i})$ has a corresponding visual element produced by evaluating the graphic section on the graphic base space $\gsection|_{\gbase_{i}}$. In \autoref{fig:atct:morphisms:sheaf} the output of $\gsection$ as pixels in an idealized prerendered space is approximated as the circles. Each graphic section $\gsection(\gbasepoint), \gbasepoint \in \gbase_{i}$ that is a piece of the graphic has a corresponding pulled back data value $\vindexpull\dsectionc(\gbasepoint)$. The pullback copies the data points such that $\vindexpull\dsectionc|_{\gbase_i} = \dsection(\dbasepoint_i)$. Each visual element $\gsection|_{\gbase_i}$ is generated from a single record $\dsection(\dbasepoint_i)$; therefore the pushforward is the curried graphic section $\gsection|_{\vindexpre(\dbasepoint_i)}$. The graphic parameterized in \autoref{fig:atct:morphisms:sheaf} is intended as an approximation of $\vindexpush\gsection$.
